
### Data preparation

Before running the statistical analysis, the dataset was checked to make sure the data were complete and organized correctly.

The experiment originally included:

- three groups: `ap`, `cp`, and `pp`
- three ID conditions: `ID1`, `ID2`, and `ID3`
- up to three repetitions: `R1`, `R2`, and `R3`

However, not all participants completed every ID condition and every repetition. Therefore, the dataset had to be checked for missing or incomplete conditions before creating the final dataset used for the analysis.

The groups are:

- `ap` = healthy adult group
- `cp` = healthy young group
- `pp` = stroke group


#### Import and inspect the data

The raw dataset was first imported and inspected to understand its structure, variables, and dimensions.

```{r}
data_raw <- read.table("data/Results.csv", header = TRUE)

head(data_raw) # display data
```
```{r}
str(data_raw) # structure of data
```
```{r}
dim(data_raw) # dimension of data (rows, columns)
```

#### Check GROUP × ID completeness

Next, the number of observations/rows for each combination of `GROUP` and `ID`:

```{r}
data_raw %>%
  count(GROUP, ID)
```
For the `ap` group, `ID1`, `ID2`, and `ID3` each contain 740 observations. For the `cp` group, all three IDs each contain 1140 observations. This shows that the three ID conditions are complete within these two groups.

For the stroke group (`pp`), `ID1` and `ID2` each contain 760 observations, while `ID3` contains only 400 observations. This shows that `ID3` is incomplete for the `pp` group because some stroke participants did not complete this condition.

Therefore, `ID3` will be removed before the ANOVA analysis so that the same ID conditions are available across all three groups.


#### Remove the incomplete ID3 condition

The previous check showed that `ID3` was incomplete for the stroke group (`pp`). Therefore, all observations belonging to `ID3` were removed before continuing the analysis.

```{r}
data_clean <- data_raw %>%
  filter(ID != "ID3")

head(data_clean)
```

#### Check repetitions




#### Check participants by GROUP

#### Create the cleaned dataset