
### Data preparation

Before running the statistical analysis, the dataset was checked to make sure the data were complete and organized correctly.

The experiment originally included:

- three groups: `ap`, `cp`, and `pp`
- three ID conditions: `ID1`, `ID2`, and `ID3`
- up to three repetitions: `R1`, `R2`, and `R3`

However, not all participants completed every ID condition and every repetition. Therefore, the dataset had to be checked for missing or incomplete conditions before creating the final dataset used for the analysis.

The groups are:

- `ap` = healthy adult group
- `cp` = healthy young group
- `pp` = stroke group


#### Import and inspect the data

The raw dataset was first imported and inspected to understand its structure, variables, and dimensions.

```{r}
data_raw <- read.table("data/Results.csv", header = TRUE)

head(data_raw) # display data
```
```{r}
str(data_raw) # structure of data
```
```{r}
dim(data_raw) # dimension of data (rows, columns)
```

#### Check GROUP × ID completeness




#### Check repetitions

#### Check participants by GROUP

#### Create the cleaned dataset