
## Run the linear regression by GROUP

The aim is to see how MovementTime changes when the difficulty (ID) increases, and whether this change is different between the three groups.

A separate linear regression is calculated for each group:

ap = healthy adults

cp = healthy young adults

pp = stroke group

The regression equation is:

$y = mx + b$

$MT = a + b(ID)$

where:

MT = Movement Time

a = intercept

b = slope

ID = Index of Difficulty

The slope tells us how much Movement Time changes when ID increases.

### Regression equations

For the ANOVA, `ID` was treated as a categorical variable with two conditions: `ID1` and `ID2`.

For the linear regression, we need to convert the categorical `ID` variable to a numerical variable with the actual Index of Difficulty values:

- `ID1` = 3.80
- `ID2` = 5.43

A new variable called `ID_numeric` is therefore created:

```{r}
regression_data <- S %>%
  mutate(ID_numeric = case_when(ID == "ID1" ~ 3.80, ID == "ID2" ~ 5.43))
# mutate() creates the new column `ID_numeric`.
# case_when()` replaces each ID condition with its corresponding numerical value


# Check that the correct numerical value was assigned to each ID
regression_data %>% distinct(ID, ID_numeric)
```

The original `ID` column is kept, while `ID_numeric` is added for the regression analysis.


A separate linear regression is then calculated for each group:

```{r}

# lm = linear model, MT = y & ID_numeric = x.


# 1. Healthy adult group
regression_ap <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "ap")) # only keep rows where GROUP is ap

# 2. Healthy young group
regression_cp <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "cp")) # only keep rows where GROUP is "cp".

# 3. Stroke group
regression_pp <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "pp")) # only keep rows where GROUP is "pp".


show(regression_ap)
show(regression_cp)
show(regression_pp)
```

For each regression:

- `MT` is the Movement Time
- `ID_numeric` is the numerical Index of Difficulty
- `filter()` selects only one group

Therefore, one regression equation is calculated separately for `ap`, `cp`, and `pp`.

The regression equations are:

**Healthy adults (`ap`):** $MT = 0.372 + 0.165(ID)$

**Healthy young adults (`cp`):** $MT = 0.366 + 0.123(ID)$

**Stroke group (`pp`):** $MT = -0.259 + 0.898(ID)$

All three slopes are positive. This means that Movement Time increases when the Index of Difficulty increases.

The stroke group (`pp`) has the largest slope (`0.898`). This means that Movement Time increases more strongly with difficulty in the stroke group than in the two healthy groups.

## Save a graph in a PDF file for publication

### Create the publication figure


## Export the graph as a PDF file for publication