
## Run the linear regression by GROUP

The aim is to see how MovementTime changes when the difficulty (ID) increases, and whether this change is different between the three groups.

A separate linear regression is calculated for each group:

ap = healthy adults

cp = healthy young adults

pp = stroke group

The regression equation is:

$y = mx + b$

$MT = a + b(ID)$

where:

MT = Movement Time

a = intercept

b = slope

ID = Index of Difficulty

The slope tells us how much Movement Time changes when ID increases.

### Regression equations

For the ANOVA, `ID` was treated as a categorical variable with two conditions: `ID1` and `ID2`.

For the linear regression, we need to convert the categorical `ID` variable to a numerical variable with the actual Index of Difficulty values:

- `ID1` = 3.80
- `ID2` = 5.43

A new variable called `ID_numeric` is therefore created:

```{r}
regression_data <- S %>%
  mutate(ID_numeric = case_when(ID == "ID1" ~ 3.80, ID == "ID2" ~ 5.43))
# mutate() creates the new column `ID_numeric`.
# case_when()` replaces each ID condition with its corresponding numerical value


# Check that the correct numerical value was assigned to each ID
regression_data %>% distinct(ID, ID_numeric)
```

The original `ID` column is kept, while `ID_numeric` is added for the regression analysis.


A separate linear regression is then calculated for each group:

```{r}

# lm = linear model, MT = y & ID_numeric = x.


# 1. Healthy adult group
regression_ap <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "ap")) # only keep rows where GROUP is ap

# 2. Healthy young group
regression_cp <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "cp")) # only keep rows where GROUP is "cp".

# 3. Stroke group
regression_pp <- lm(MT ~ ID_numeric, data = regression_data %>% filter(GROUP == "pp")) # only keep rows where GROUP is "pp".


show(regression_ap)
show(regression_cp)
show(regression_pp)
```

For each regression:

- `MT` is the Movement Time
- `ID_numeric` is the numerical Index of Difficulty
- `filter()` selects only one group

Therefore, one regression equation is calculated separately for `ap`, `cp`, and `pp`.

The regression equations are:

**Healthy adults (`ap`):** $MT = 0.372 + 0.165(ID)$

**Healthy young adults (`cp`):** $MT = 0.366 + 0.123(ID)$

**Stroke group (`pp`):** $MT = -0.259 + 0.898(ID)$

All three slopes are positive. This means that Movement Time increases when the Index of Difficulty increases.

The stroke group (`pp`) has the largest slope (`0.898`). This means that Movement Time increases more strongly with difficulty in the stroke group than in the two healthy groups.

## Save a graph in a PDF file for publication

A graph is created to show how mean Movement Time changes with ID for each group.

The graph includes:

- the mean Movement Time for each ID
- one line for each group
- error bars showing the variability
- dashed regression lines
- the regression equation for each group

This allows the measured data and the linear regression results to be compared visually.

### Create the publication figure

First, the mean Movement Time and standard deviation are calculated for each `GROUP × ID` combination:

```{r}

publication_data <- regression_data %>% group_by(GROUP, ID_numeric) %>%
  summarise(mean_MT = mean(MT), sd_MT = sd(MT), .groups = "drop")

show(publication_data)

```

This creates one row for each group and ID containing:

- `mean_MT` = average Movement Time
- `sd_MT` = standard deviation of Movement Time


`GROUP` is converted to a factor to explicitly tell R that it contains categories. The levels are ordered as `pp`, `ap`, and `cp` so that the groups appear in this same order in the graph and legend:

```{r}

publication_data$GROUP <- factor(publication_data$GROUP, levels = c("pp", "ap", "cp"))

```

## Export the graph as a PDF file for publication

The publication graph is created using `publication_data`:

```{r}

# 2. Create the ggplot
publication_plot <- ggplot(interaction_data, aes(x = ID_numeric, y = mean_MT, color = GROUP)) +
  
  # 3. Dashed regression lines across the full x-axis
  geom_smooth(aes(group = GROUP), method = "lm", se = FALSE, # don't draw confidence intervals
              fullrange = TRUE, linetype = "dashed", linewidth = 0.5) + 
              # extend regression line beyond full range 
  
  # 4. Solid line connecting the two measured mean values
  geom_line(aes(group = GROUP), linewidth = 0.6) +
  
  # 5. Error bars showing mean ± 0.5 SD
  geom_errorbar(aes(ymin = mean_MT - 0.5 * sd_MT,
                    ymax = mean_MT + 0.5 * sd_MT),
                width = 0.08) +
  
  # Mean values
  geom_point(shape = 21, fill = "white", size = 3, stroke = 1) +
  
  # Regression equations
  annotate("text", x = 0.5, y = 5.5, label = "MT = -0.259 + 0.898 * ID",
           color = "red", hjust = 0, size = 4) +
  annotate("text", x = 0.5, y = 4.5, label = "MT = 0.372 + 0.165 * ID",
           color = "green3", hjust = 0, size = 4) +
  annotate("text", x = 0.5, y = 3.5, label = "MT = 0.366 + 0.123 * ID",
           color = "blue", hjust = 0, size = 4) +
  
  # Axes and legend
  scale_x_continuous(name = "ID", breaks = 0:6, limits = c(0, 6.3)) +
  scale_y_continuous(name = "Mean Movement Time (s)", limits = c(-1.3, 6.7)) +
  
  # Group colors
  scale_color_manual(values = c("pp" = "red", "ap" = "green3", "cp" = "blue")) +
  
  labs(color = "GROUP") +
  theme_minimal()

show(publication_plot)

```
The **solid lines** connect the measured mean values for `ID1` and `ID2`.

The **dashed lines** show the linear regression for each group.

The error bars show:

$Mean \pm 0.5 \times SD$

Larger error bars mean that the Movement Time values are more spread out around the mean.


### Interpretation

Movement Time increases with ID in all three groups, but the increase is much larger for the stroke group (`pp`). The `ap` and `cp` groups show smaller and relatively similar increases.

The `pp` group also shows much greater variability in Movement Time, as indicated by its larger error bars, whereas the healthy groups have smaller error bars and more consistent values.

Overall, the figure visually supports the regression results and the `GROUP × ID` interaction described previously.





